GSE74548: Gene Methylation Enrichment Analysis

### 2022-05-11 gmea.Rmd
adjustments for dma3 (hcy)

# DM1 - post trial supplement versus placebo

@@

```{r,dma1a}

dm <- read.table("dma1a.tsv")
head(dm,50) %>%
  kbl(caption = "Top significant genes with limma") %>%
  kable_paper("hover", full_width = F)

@@

mitch_report(res,outfile="dma1a_mitch.html",overwrite=TRUE)

@@

dm <- read.table("dma1a.tsv")
dm <- subset(dm,Regulatory_Feature_Group == "Promoter_Associated")
dm$adj.P.Val <- p.adjust(dm$P.Value)

@@

mitch_report(res,outfile="dma1a_mitch_promo.html",overwrite=TRUE)

>>>>

# DM3 - post trial supplement versus placebo

@@

```{r,dma3a}

dm <- read.table("dma3a.tsv")

# testing
dm <- head(dm,40000)

@@

mitch_report(res,outfile="dma3a_mitch.html",overwrite=TRUE)

@@

dm <- read.table("dma3a.tsv.gz")
dm <- subset(dm,Regulatory_Feature_Group == "Promoter_Associated")

# testing
dm <- head(dm,20000)

dm$adj.P.Val <- p.adjust(dm$P.Value)

@@

mitch_report(res,outfile="dma3a_mitch_promo.html",overwrite=TRUE)
